Escape Analysis and Specialization in a Tracing JIT

### 2010-09-22 talk/pepm2011/paper.tex
Two typos.

Type dispatching is the process of finding the concrete implementation that is
applicable to the objects at hand when doing a generic operation at hand. An
example would be the addition of two objects: The addition needs to check what
the concrete objects are that should be added are, and choose the implementation
that is fitting for them.

>>>>

Type dispatching is the process of finding the concrete implementation that is
applicable to the objects at hand when doing a generic operation on them. An
example would be the addition of two objects: The addition needs to check what
the concrete objects that should be added are, and choose the implementation
that is fitting for them.
